%-------------------------
% Resume in LaTeX
% Template: Jake's Resume (sb2nov/resume) — ATS-friendly, single-column
% Author: Samar Hayat
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontspec}
\setmainfont{Ubuntu}[
  Path=/usr/share/fonts/ubuntu/,
  Extension=.ttf,
  UprightFont=Ubuntu-R,
  BoldFont=Ubuntu-B,
  ItalicFont=Ubuntu-RI,
  BoldItalicFont=Ubuntu-BI,
]

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Samar Hayat} \\ \vspace{1pt}
    \small
    Islamabad, Pakistan \textbar{}
    \href{mailto:samarhayat.dev@gmail.com}{samarhayat.dev@gmail.com} \textbar{}
    +92 349 5129992 \\
    \href{https://www.thesamarhayat.com/}{thesamarhayat.com} \textbar{}
    \href{https://github.com/thesamarhayat}{github.com/thesamarhayat} \textbar{}
    \href{https://www.linkedin.com/in/thesamarhayatt}{linkedin.com/in/thesamarhayatt}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{
  Frontend Developer with 2.5+ years of experience building fast, responsive, pixel-perfect web applications using \textbf{React.js}, \textbf{Next.js}, and \textbf{TypeScript}. Based in Islamabad, Pakistan; open to remote. Skilled in \textbf{Tailwind CSS}, \textbf{ShadCN}, and \textbf{MUI}; integrates \textbf{GraphQL}, \textbf{REST}, and APIs (LinkedIn, Meta, TikTok, Amadeus, Stripe, WhatsApp). Currently at GlobeWyze Inc.; previously at Xecutors, Citadel Solutions, and ZITSOL.
}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {GlobeWyze Inc.}{Oct 2025 -- Present}
      {Frontend Developer}{Islamabad, Pakistan}
      \resumeItemListStart
        \resumeItem{Build responsive React.js and Next.js applications with TypeScript, translating Figma designs into pixel-perfect, accessible UI.}
        \resumeItem{Integrate GraphQL APIs and optimize component performance; collaborate with backend engineers to ship production features on schedule.}
      \resumeItemListEnd

    \resumeSubheading
      {GlobeWyze Inc.}{Aug 2025 -- Oct 2025}
      {QA Engineer}{Islamabad, Pakistan}
      \resumeItemListStart
        \resumeItem{Tested React-based UI components for pixel-perfect Figma alignment across desktop, tablet, and mobile viewports.}
        \resumeItem{Documented UI/UX inconsistencies and partnered with frontend developers to resolve bugs before production release.}
      \resumeItemListEnd

    \resumeSubheading
      {Xecutors}{Jul 2024 -- Jun 2025}
      {Assistant Website Developer}{Chakwal, Pakistan}
      \resumeItemListStart
        \resumeItem{Built production web apps with Next.js, React.js, Tailwind CSS, and ShadCN; integrated LinkedIn, Meta, and TikTok APIs via GraphQL (Nhost, Hasura, Apollo Client).}
        \resumeItem{Optimized applications for SEO and Core Web Vitals in collaboration with design and backend teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Citadel Solutions}{May 2024 -- Jul 2024}
      {Website Developer}{Lahore, Pakistan}
      \resumeItemListStart
        \resumeItem{Delivered client WordPress websites with custom JavaScript, on-page SEO, and responsive mobile-friendly layouts.}
      \resumeItemListEnd

    \resumeSubheading
      {ZITSOL}{Nov 2023 -- Apr 2024}
      {Junior Website Developer}{Chakwal, Pakistan}
      \resumeItemListStart
        \resumeItem{Built WordPress sites with Elementor and Gutenberg; applied Tailwind CSS, SEO, and performance optimizations across responsive layouts.}
      \resumeItemListEnd

    \resumeSubheading
      {ZITSOL}{Aug 2023 -- Oct 2023}
      {Website Developer Intern}{Chakwal, Pakistan}
      \resumeItemListStart
        \resumeItem{Developed responsive pages with HTML5, CSS3, JavaScript, and Tailwind CSS during structured WordPress and SEO internship.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{NoteSeek} $|$ \emph{Next.js, NestJS, Prisma, Supabase, Stripe} $|$ Private (demo on request)}{}
          \resumeItemListStart
            \resumeItem{Contributed to NestJS BFF API and Next.js frontend for a telehealth platform with PHIPA-compliant auth, Stripe payments, Socket.io real-time queues, and multi-role access (patient, provider, clinic admin).}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Fynnexa} $|$ \emph{Next.js, NestJS, Microservices, AWS, Supabase} $|$ Private (demo on request)}{}
          \resumeItemListStart
            \resumeItem{Contributed to a 10-service NestJS microservices backend and Next.js 15 frontend for deal management, KYC onboarding, real-time chat, AWS Bedrock AI assistant, and Stripe-powered payments.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Gogency} $|$ \emph{Next.js, React, TypeScript, Tailwind CSS, ShadCN UI} $|$ \href{https://gogency.com}{\underline{gogency.com}}}{}
          \resumeItemListStart
            \resumeItem{Built frontend features for an automated travel agency platform with ticket invoicing, email automation, HR management, and one-click website generation using Next.js, TypeScript, and ShadCN UI.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Silk Travels} $|$ \emph{React, Tailwind CSS, REST APIs} $|$ \href{https://www.silktravels.co.uk/}{\underline{silktravels.co.uk}}}{}
          \resumeItemListStart
            \resumeItem{Built travel booking front end at Xecutors using Gogency templates; integrated Amadeus, Stripe, Gmail, and WhatsApp APIs for flight search, payments, and consultant workflows.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Xecutors} $|$ \emph{Next.js, Tailwind CSS} $|$ \href{https://www.xecutors.com}{\underline{xecutors.com}}}{}
          \resumeItemListStart
            \resumeItem{Contributed to the company website with Next.js and Tailwind CSS; refined UI components, improved page performance, and implemented responsive landing page sections.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend}{: React.js, Next.js, TypeScript, JavaScript (ES6+), HTML5, CSS3, Tailwind CSS, ShadCN UI, Material UI} \\
     \textbf{APIs \& Data}{: GraphQL, REST, Apollo Client, Nhost, Hasura, Supabase, NestJS, Postman} \\
     \textbf{Tools \& Platforms}{: Git, GitHub, Bitbucket, Figma, Jira, Vercel, WordPress, Elementor, Docker, SEO}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
